leading_cause_of_death_overall

### 2024-03-14 scripts/leading_cause_of_death.Rmd
Created simulated data and tests
Created tests for simulated data and for leading cause of death.

```{r}
# libraries
library(dplyr)
library(knitr)
library(ggplot2)
library(forcats)

@@

>>>>

```{r}
# libraries
library(dplyr)
library(knitr)
library(ggplot2)
library(forcats)
library(testthat)

@@

```{r}
# Tests

# Data set has been loaded correctly
test_that("Dataset has been loaded", {
  expect_true(exists("nyc_data"))
  expect_is(nyc_data, "data.frame")
})

# 'death_count_by_cause' has the correct columns
test_that("'death_count_by_cause' has correct columns", {
  expected_cols <- c("Leading.Cause", "Total_Deaths")
  expect_equal(colnames(death_count_by_cause), expected_cols)
})

# 'death_count_by_cause' table has correct number of rows
test_that("'death_count_by_cause' has correct number of rows", {
  expect_true(nrow(death_count_by_cause) > 0)
})
